Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
re-wrote the intro

Modern implementations of embedded control have proliferated with the
availability of low cost devices that can perform simple tasks for linear
control, spanning many areas such as environmental control and robotic
manipulations~\cite{astrom1997computer,Franklin15}.  The downside to this
approach is that in order to achieve low prices, devices are often limited
in their capabilities, be it a low number of gates in an FPGA or short word
lengths for microcontrollers.  In most cases, a floating-point implementation
is not feasible and the system can benefit from the added resolution of a
fixed-point representation.  The ubiquity of these devices requires that
they have a robust design that ensures the correct behaviour in a number of
different environments.
%
% For this reason it is
% necessary to provide design tools that formally verify the correctness
% of the digital controller.

There has been previous work to formally verify uncertain linear systems
stability in digital controllers with considerations to the implementation
aspects ({\it i.e.}, fixed-point arithmetic and word-length)~\cite{Bessa16}. 
In particular, Bessa {\it et al.} consider finite-word length (FWL) effects
over digital controllers and also parameter uncertainties in the context of
verifying the (so-called) robust non-fragile
stability~\cite{bhattacharyya97}.  However, the authors do not consider the
compete range of approximations, related to time discretisation, and
quantisation effects.  As a result, the stability verification method
proposed by Bessa {\it et al.} is incomplete, given that false alarms can be
produced due to quantisation effects.  Additionally, the authors do not
find a parametric solution for a digital controller given as a continuous
plant specification, in order to synthesise the controller implementation.

Our work makes two major contributions. First, we explore the automatic synthesis 
of {\em correct-by-construction} digital controllers, which reduces the development
cost and design time for a number of models.  In particular, we are
interested in synthesising controllers for {\em hybrid closed-loop systems},
{\it i.e.}, embedded controllers along with a model of their physical
environment (the plant), which are {\em stable}.  Due to the complexity of
such systems, we focus on linear models with known configurations to perform
parametric synthesis of the controller dynamics.

Second, since the digital control synthesis is performed over a hybrid model, 
where the plant displays a continuous behaviour and the controller operates in
both discrete time and state-space, we initially translate the problem into
a single domain, which represents a bi-simulation of the original dynamics. 
Given our primary interest in evaluating digital effects in addition to
stability, we have modelled a digital equivalent of the plant by evaluating
the effects of the quantisers (A/D and D/A converters) as time
discretisation elements with quantisation noise.  The resulting closed loop
system is a program loop working over bit-vectors of fixed-point arithmetic
with fixed word length.  The deterministic effect of the FWL is considered
and quantization errors are included in the model as an additive uncertainty, 
which must be taken into account for the correct synthesis of the robust controller
for linear systems with parametric uncertainties.

@@

We have presented a CEGIS-based approach that uses inductive synthesis in
conjunction with a robust algorithm for verifying closed-loop stability to
compute a parametric solution for a digital controller given a continuous
(or discrete) plant specification.  This enables us to automatically
synthesize correct-by-construction digital controllers for a given model of
their physical environment.  Our approach addresses the effects of the
quantisers (A/D and D/A converters) as time discretisation elements with
quantisation noise.  Our experimental results show that our CEGIS-based
approach is able to synthesise stable controllers in most benchmarks within
reasonable time frames fully automatically.
%
% and can be 
%complemented using the interval arithmetic back-end, where the inductive conjectures fail. 
%Both back-ends enabled controller synthesis for all benchmarks within reasonable time frames.
%
Future work will be the extension of this CEGIS-based approach for different
classes of systems (e.g., state-space).  We will also consider performance
requirements while synthesising the digital controller.

>>>>

Modern implementations of embedded control have proliferated with the
availability of low-cost devices that can perform highly non-trivial control
tasks, with impact in numerous application areas such as environmental
control and robotics~\cite{astrom1997computer, Franklin15}.

Correct control is non-trivial, however. The problem is exacerbated by
artefacts specific to digital control such as the effects of
finite-precision arithmetic, time discretisation, and quantisation noise
introduced by A/D and D/A conversion.  Thus, the programming is a key
barrier to broad adoption of digital control, and requires considerable
expertise.

There has been plenty of previous work that aims at \emph{verifying} a given
controller designed by the engineer.  Recent work can show the stability
digital controllers with considerations to implementation aspects, i.e.,
fixed-point arithmetic and the word length used~\cite{Bessa16}.  This work
exploits advances in bit-accurate verification of C programs to obtain a
verifier for software-implemented digital control.

By contrast, we propose to leverage very recent step-change in \emph{program
synthesis}.  Program synthesis engines use a program specification as the
starting point, and subsequently generate a sequence of candidate programs. 
The candidate programs are iteratively refined to match the specification
more closely.  Program synthesisers that implement Counter-Example Guided
Inductive Synthesis (CEGIS)~\cite{sketch} are now able to generate programs
for highly non-trivial specifications with a very high degree of automation. 
Modern CEGIS engines implement combinations of automated testing, genetic
algorithms and SMT-based automated reasoning~\cite{DBLP:conf/lpar/DavidKL15,
DBLP:conf/cav/0001A14}.

By applying a state-of-the-art CEGIS engine we are now able to present a
tool that automatically \emph{generates} digital controllers for a given
plant model that are correct by construction.  This approach promises to
reduce the cost and time of development of digital control dramatically, and
requires considerably less expertise than methodologies driven by
verification.  Specifically, we synthesise controllers for hybrid
closed-loop systems, i.e., software-implemented embedded controllers along
with a model of their physical environment (the plant), that are
\emph{stable}.  Due to the complexity of such systems, we focus on linear
models with known configurations to perform parametric synthesis of the
controller dynamics.

Our work addresses particularly challenging aspects of the control synthesis
problem.  We perform digital control synthesis over a hybrid model, where
the plant exhibits continuous behaviour and the controller operates in both
discrete time and state-space.  The key insight of our approach is that the
problem can be translated into a \emph{single, joint domain}, which
represents a bi-simulation of the original, hybrid dynamics.  Given our
primary interest in stability despite digitisation effects, we have modelled
a digital equivalent of the plant by evaluating the effects of the
quantisers (A/D and D/A converters) as time discretisation elements with
quantisation noise.  The resulting closed-loop system is a program loop that
operates on bit-vectors encoded using fixed-point arithmetic with fixed word
length (FWL).  We calculate the deterministic effect of the FWL and
quantization errors are included in the model as an additive uncertainty,
which is taken into account during the synthesis of the controller.

In summary, this paper makes the following original contributions.
%
\begin{itemize}

\item TODO 1

\item TODO 2

\end{itemize}

@@

We have presented a CEGIS-based approach that uses inductive synthesis in
conjunction with a robust algorithm for verifying closed-loop stability to
compute a parametric solution for a digital controller given a continuous
(or discrete) plant specification.  This enables us to automatically
synthesize correct-by-construction digital controllers for a given model of
their physical environment.  Our approach addresses the effects of the
quantisers (A/D and D/A converters) as time discretisation elements with
quantisation noise.  Our experimental results show that our CEGIS-based
approach is able to synthesise stable controllers in most benchmarks within
reasonable time frames fully automatically.
%
% and can be 
%complemented using the interval arithmetic back-end, where the inductive conjectures fail. 
%Both back-ends enabled controller synthesis for all benchmarks within reasonable time frames.
%
Future work will be the extension of this CEGIS-based approach to further
classes of systems.  We will also consider performance requirements while
synthesising the digital controller.
